---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/playdoh.svg?branch=master)](https://travis-ci.org/hrbrmstr/playdoh) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/playdoh/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/playdoh)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/playdoh)](https://cran.r-project.org/package=playdoh)

# playdoh

Make 'DNS over HTTPS' Queries

## Description

Make 'DNS over HTTPS' Queries

DoH RTFM: <https://tools.ietf.org/id/draft-ietf-doh-dns-over-https-05.html>

## What's Inside The Tin

The following functions are implemented:

### Utility

- `to_inaddr_arpa`:	Convert a vector of IPv4 addresses to in-addr.arpa format

### DoH

- `doh_get`: Make a DoH Request (GET/REST)

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://sr.ht.com/~hrbrmstr/playdoh.git")
# or
devtools::install_gitlab("hrbrmstr/playdoh.git")
# or (if you must)
devtools::install_github("hrbrmstr/playdoh")
```

## Usage

```{r lib-ex}
library(playdoh)
library(tidyverse) # for printing

# current version
packageVersion("playdoh")

```

### Basic functionality

```{r doh2}
doh_get("apple.com", "A")

doh_get("rud.is", "AAAA")

doh_get("rud.is", "MX")

doh_get("lenovo.com", "TXT")

doh_get("dataassurance.pwc.com", "CNAME")

doh_get("rud.is", "NS")

doh_get("rud.is", "SOA")

doh_get(to_inaddr_arpa("104.244.13.104"), "PTR")
```

## playdoh Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
